---
title: "Data 607 Project 1"
author: "Wilson Chau"
date: "2022-09-24"
output: html_document
---
# Introduction:
In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:
Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents
For the first player, the information would be:
Gary Hua, ON, 6.0, 1794, 1605

My goal is to create the same format as above. 
Name, State, Total Points, Pre-rating scores, and Avg Opp Pre-rating
Load up the library and preview data
```{r setup, include=FALSE}
require(dplyr)
require(readr)
require(tidyr)
require(stringr)
require(knitr)
load_txt <- readLines("https://raw.githubusercontent.com/Wilchau/Data607Project1/main/tournamentinfo.txt")
head(load_txt)
```
## Cleaning:
The data is unorganized, and i see that line 1 is occupied. The format is also not properly formatted or cleaned up. I use the str_locate function to help find the starting and ending positon of a specificed pattern. I also generate sequences to be used in extracting required field.

```{r}
c0 <- 0
c1 <- unname(str_locate_all(pattern = '\\|', load_txt[5])[[1]][1,1])
c2 <- unname(str_locate_all(pattern = '\\|', load_txt[5])[[1]][2,1])
c3 <- unname(str_locate_all(pattern = '\\|', load_txt[5])[[1]][3,1])
c4 <- max(nchar(load_txt))
d1 <- seq(5, 196, 3) 
d2 <- seq(6, 196, 3)   

f1 <- load_txt[d1] 
f2 <- load_txt[d2]     
```
## Extracting fields:
This allows us to extract field and load it into the dataframe.
I focus on taking the player's name and state first and extracting them into chess_data
```{r}
name <- substr(f1, c1+1, c2-2)
name <- str_trim(name)
Player_Name <- str_to_title(name) 
s_raw <- substr(d2, c0, c1-1)
State <- str_trim(s_raw)
chess_data <- data.frame(Player_Name, State)
```
## Extracting fields part 2:
I focus on taking points, and total points and extract them into one
```{r}
point <- substr(f1, c2+1, c3-1)        
chess_data$TotalPoints <- sprintf("%.1f", as.numeric(point))
pre <- substr(f2, c1+1, c2-1)
pre <- str_extract(pre, ': *\\d{2,}')    
chess_data$PreRating <- as.integer(str_extract(pre, '\\d{2,}'))
```
## Calculate Pre-rating opponent scores:
To calculate the average Pre-rating of opponent 
I work on using a nested loop for this scenario, while adding in the sequences.This should help generate the sequences of pre-rating.
I use head() to see that this table is the correct format of the request from the introduction.
 
```{r}
oppenent <- substr(d1, c3+1, c4)
oppenent <- str_extract_all(oppenent, '\\b\\d{1,}')
oppenent <- as.matrix(oppenent)

calculate <- function(z, p) {
    temp <- z[p]
    
    for (place in temp){
        rate <- 0
        c <- 0
        for(i in place) {
            c <- c + 1
            rate <- rate + chess_data$PreRating[as.numeric(i)]
        }
        rate <- round(rate / c) #This will calculate the average
        
    }
    return(rate)
}
chess_data$AvgOppPreRating <- apply(oppenent, 1, calculate)

head(chess_data) 
```
#Conversaion:
Converting this output to .csv file
```{r}
write.csv(chess_data,"Chess_Tournament.csv")
```